---
title: "ROAPS K simulations"
author: "Erika Mudrak"
output: html_document
---

Simulations of theoretical models- Population growth over random period of years (uniform distrib 0 to 100 yrs since last disturbance)

* density independent, fixed r
    + $N_{t} = N_{0}e^{rt}$
    + N0 = 5, r = 0.06, t~Unif(0,100)  
* density dependent - fixed K, fixed r
    + $N_{t} = \frac{KN_{0}e^{rt}}{K+N_{0}(e^{rt}-1)}$
    + N0=5, r=0.06, t~Unif(0,100) K=100  
* Random K, fixed r
    + $N_{t} = \frac{KN_{0}e^{rt}}{K+N_{0}(e^{rt}-1)}$)
    + N0=5, r=0.06, t~Unif(0,100) K~Unif(1,100)
* Random K, random r
    + $N_{t} = \frac{KN_{0}e^{rt}}{K+N_{0}(e^{rt}-1)}$
    + N0=5, r~unif(0.02, 0.1), t~Unif(0,100) K~Unif(1,100)

------------

Code to produce communities
```{r Model}

NUMSITES=100                  # Generate abundances for 100 sites
r=0.06                        # Set constant r 
N0=5                          # Set Initial pop size
t=runif(NUMSITES, 0,100)      # 100 different values of t ranging from 0 to 100

# Density Independent Model
DensInd=round(N0*exp(r*t))    # 100 different abundances

# Density Dependent Model
K=100                         # Set constant K
ConstK=round((K*N0*exp(r*t))/(K+N0*(exp(r*t)-1)))

# Random K Model
k_rand=runif(NUMSITES, 1,100) # 100 random values for k
RandK=round((k_rand*N0*exp(r*t))/(k_rand+N0*(exp(r*t)-1)))

# Random K and r Model
r_rand=runif(NUMSITES, 0.02, 0.1) # 100 random values for r
RandKr=round((k_rand*N0*exp(r_rand*t))/(k_rand+N0*(exp(r_rand*t)-1)))

```

\newpage

Plot a single curve set of ROAPs

```{r plotting, echo=FALSE, fig.height=4, fig.width=6}
# Make a function to arrange list in plotting form
RankCurve=function(x)  {
  x=as.matrix(x)
  cbind(Rank=1:length(x), Abund=sort(x, decreasing=T))
  }

par(mar=c(5,4,1,2)+0.1)


MaxAbund=max(DensInd, ConstK, RandK, RandKr)
  
plot(c(1,NUMSITES),c(1,MaxAbund),pch=NA, main=NA, ylab="Abundance",log="y", xlab="Rank Abundance")
lines(RankCurve(DensInd), col="red")
lines(RankCurve(ConstK), col="darkgreen")
lines(RankCurve(RandK),col="blue")
lines(RankCurve(RandKr), col="orange")

text(c(60, 35, 35, 20), c(500, 100, 50, 20), c("Density Independent", "Fixed K","Random K", "Random K and r"), col=c("red","darkgreen","blue","orange"))

```

Repeat this process 100 times to make 100 generated metacommunities (1 ROAP each)

```{r, echo=FALSE, fig.height=4, fig.width=6}


REPS=100
NUMSITES=100
r=0.06
N0=5
K=100

allDensInd=allConstK=allRandK=allRandKr=data.frame(matrix(NA, nrow=NUMSITES, ncol=REPS))
names(allDensInd)=names(allConstK)=names(allRandK)=names(allRandKr)=paste("Rep", 1:REPS)

par(mar=c(5,4,1,2)+0.1)
MaxAbund=max(DensInd, ConstK, RandK, RandKr)
plot(c(1,NUMSITES),c(1,MaxAbund),pch=NA, main=NA, ylab="Abundance",log="y", xlab="Rank Abundance")  

for (i in 1:REPS){
t=runif(NUMSITES, 0,100)
allDensInd[i]=round(N0*exp(r*t))
allConstK[i]=round((K*N0*exp(r*t))/(K+N0*(exp(r*t)-1)))
k_rand=runif(NUMSITES, 1,100)
allRandK[i]=round((k_rand*N0*exp(r*t))/(k_rand+N0*(exp(r*t)-1)))
r_rand=runif(NUMSITES, 0.02, 0.1)
allRandKr[i]=round((k_rand*N0*exp(r_rand*t))/(k_rand+N0*(exp(r_rand*t)-1)))
lines(RankCurve(allDensInd[i]), col="red")
lines(RankCurve(allConstK[i]), col="darkgreen")
lines(RankCurve(allRandK[i]),col="blue")
lines(RankCurve(allRandKr[i]), col="orange")
}


```

\newpage

Plot filled envelopes instead of indivudual lines.  Here, we show the min and max of all simulated communities (though we could show 5% and 95%).

Since the Random K and the Random K and R models overlap so much, I'm not sure how to do this. Especially in black and white. Suggestions?

```{r envelopes, echo=FALSE}

RankEnvelope=function(x){
  xsort=apply(x, 2, sort, decreasing=T)
  xmax=apply(xsort,1, quantile, probs=0.95)
  xmin=apply(xsort,1, quantile, probs=0.05)
  return(data.frame(max=xmax, min=xmin))
}




tiff("MS/Envelopes.tiff",  600, 450)
par(mar=c(5,4,1,2)+0.1)
MaxAbund=max(allDensInd, allConstK, allRandK, allRandKr)
plot(c(1,NUMSITES),c(1,MaxAbund),pch=NA, main=NA, ylab="Abundance",log="y", xlab="Rank Abundance") 

# lines(RankCurve(RankEnvelope(allDensInd)$min), col="red")
# lines(RankCurve(RankEnvelope(allDensInd)$max), col="red")
# lines(RankCurve(RankEnvelope(allConstK)$min), col="darkgreen")
# lines(RankCurve(RankEnvelope(allConstK)$max), col="darkgreen")
# lines(RankCurve(RankEnvelope(allRandK)$min), col="blue")
# lines(RankCurve(RankEnvelope(allRandK)$max), col="blue")
# lines(RankCurve(RankEnvelope(allRandKr)$min), col="orange")
# lines(RankCurve(RankEnvelope(allRandKr)$max), col="orange")

polygon(rbind(RankCurve(RankEnvelope(allDensInd)$max), apply(RankCurve(RankEnvelope(allDensInd)$min),2,rev)), col=adjustcolor("red", alpha.f=0.6))
polygon(rbind(RankCurve(RankEnvelope(allConstK)$max), apply(RankCurve(RankEnvelope(allConstK)$min),2,rev)), col=adjustcolor("green", alpha.f=0.6))
polygon(rbind(RankCurve(RankEnvelope(allRandK)$max), apply(RankCurve(RankEnvelope(allRandK)$min),2,rev)), col=adjustcolor("blue", alpha.f=0.6))
# polygon(rbind(RankCurve(RankEnvelope(allRandKr)$max), apply(RankCurve(RankEnvelope(allRandKr)$min),2,rev)), col=adjustcolor("orange", alpha.f=0.6))

text(c(60, 20, 35), c(500, 150, 15), c("Density Independent", "Fixed K","Random K"), col=c("red","darkgreen","blue"))

dev.off()

mean(apply(allDensInd,2, var))
mean(apply(allDensInd,2, function(x){sd(x)/length(x)}))
mean(apply(allDensInd,2, function(x){var(log(x))}))
mean(apply(allDensInd,2, function(x){sd(log(x))/length(x)}))

mean(apply(allConstK,2, var))
mean(apply(allConstK,2, function(x){sd(x)/length(x)}))
mean(apply(allConstK,2, function(x){var(log(x))}))
mean(apply(allConstK,2, function(x){sd(log(x))/length(x)}))


mean(apply(allRandK,2, var))
mean(apply(allRandK,2, function(x){sd(x)/length(x)}))
mean(apply(allRandK,2, function(x){var(log(x))}))
mean(apply(allRandK,2, function(x){sd(log(x))/length(x)}))
```


Consider varying levels of r, but fixed for each curve, reflecting different biology traits of the species. It seems like the slope of the ROAP reflects r

```{r levels of fixed r}

# Random K Model

k_rand=runif(NUMSITES, 1,100) # 100 random values for k

r=0.008
Sp1=round((k_rand*N0*exp(r*t))/(k_rand+N0*(exp(r*t)-1)))

r=0.02
Sp2=round((k_rand*N0*exp(r*t))/(k_rand+N0*(exp(r*t)-1)))

r=0.08
Sp3=round((k_rand*N0*exp(r*t))/(k_rand+N0*(exp(r*t)-1)))


r=1
Sp4=round((k_rand*N0*exp(r*t))/(k_rand+N0*(exp(r*t)-1)))

par(mar=c(5,4,1,2)+0.1)


MaxAbund=max(Sp1, Sp2, Sp3, Sp4)
  
plot(c(1,NUMSITES),c(1,MaxAbund),pch=NA, main=NA, ylab="Abundance",log="y", xlab="Rank Abundance")
lines(RankCurve(Sp1), col="red")
lines(RankCurve(Sp2), col="darkgreen")
lines(RankCurve(Sp3),col="blue")
lines(RankCurve(Sp4), col="orange")


```

Draw K from unif(1,100), but then multiply by a constant- affects y intercept

```{r levels of fixed K}


# Random K Model
r=0.06
k_univ=runif(NUMSITES, 1,100) # 100 random values for k


k_rand=0.2*k_univ
Sp1=round((k_rand*N0*exp(r*t))/(k_rand+N0*(exp(r*t)-1)))

k_rand=0.4*k_univ
Sp2=round((k_rand*N0*exp(r*t))/(k_rand+N0*(exp(r*t)-1)))

k_rand=0.8*k_univ
Sp3=round((k_rand*N0*exp(r*t))/(k_rand+N0*(exp(r*t)-1)))


k_rand=1.2*k_univ
Sp4=round((k_rand*N0*exp(r*t))/(k_rand+N0*(exp(r*t)-1)))

par(mar=c(5,4,1,2)+0.1)


MaxAbund=max(Sp1, Sp2, Sp3, Sp4)
  
plot(c(1,NUMSITES),c(1,MaxAbund),pch=NA, main=NA, ylab="Abundance",log="y", xlab="Rank Abundance")
lines(RankCurve(Sp1), col="red")
lines(RankCurve(Sp2), col="darkgreen")
lines(RankCurve(Sp3),col="blue")
lines(RankCurve(Sp4), col="orange")




```

